---
title: "Hands on Ex04a"
---

# **1  Visual Statistical Analysis**

## **1.1 Learning Outcome**

In this hands-on exercise, I will show on to use:

-   ggstatsplot package to create visual graphics with rich statistical information,

-   performance package to visualise model diagnostics, and

-   parameters package to visualise model parameters

## **1.2 Visual Statistical Analysis with ggstatsplot**

[**ggstatsplot**](https://indrajeetpatil.github.io/ggstatsplot/) is an extension of [**ggplot2**](https://ggplot2.tidyverse.org/) package for creating graphics with details from statistical tests

## **1.3 Getting Started**

### **1.3.1 Installing and launching R packages**

```{r}
pacman::p_load(ggstatsplot, tidyverse)
```

### **1.3.2 Importing data**

```{r}
exam <- read_csv("Data/Exam_data.csv",show_col_types = FALSE)
head(exam)
```

### **1.3.3 One-sample test: *gghistostats()* method**

```{r}
set.seed(1234)

gghistostats(
  data = exam,
  x = ENGLISH,
  type = "bayes",
  test.value = 60,
  xlab = "English scores"
)
```

### **1.3.4 Two-sample mean test: *ggbetweenstats()***

```{r}
ggbetweenstats(
  data = exam,
  x = GENDER, 
  y = MATHS,
  type = "np",
  messages = FALSE
)
```

### **1.3.5 Oneway ANOVA Test: *ggbetweenstats()* method**

```{r}
ggbetweenstats(
  data = exam,
  x = RACE, 
  y = ENGLISH,
  type = "p",
  mean.ci = TRUE, 
  pairwise.comparisons = TRUE, 
  pairwise.display = "s",
  p.adjust.method = "fdr",
  messages = FALSE
)
```

### **1.3.6 Significant Test of Correlation: *ggscatterstats()***

```{r}
ggscatterstats(
  data = exam,
  x = MATHS,
  y = ENGLISH,
  marginal = FALSE,
  )
```

### **1.3.7 Significant Test of Association (Depedence) : *ggbarstats()* methods**

```{r}
exam1 <- exam %>% 
  mutate(MATHS_bins = 
           cut(MATHS, 
               breaks = c(0,60,75,85,100))
)
```

In the code chunk below, the Maths scores is binned into a 4-class variable by using [*cut()*](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/cut).

In this code chunk below [*ggbarstats()*](https://indrajeetpatil.github.io/ggstatsplot/reference/ggbarstats.html) is used to build a visual for Significant Test of Association

```{r}
ggbarstats(exam1, 
           x = MATHS_bins, 
           y = GENDER)
```
