---
title: "Hands-on_Ex02"
Published: Apil 15，2024
---

# 1. Overview

In this chapter, I will practice several ggplot2 extensions to create more elegant and effective statistical graphics.

-   control the placement of annotation on a graph by using functions provided in ggrepel package,

-   create professional publication quality figure by using functions provided in ggthemes and hrbrthemes packages,

-   plot composite figure by combining ggplot2 graphs by using patchwork package.

# 2. Getting start

### **2.1 Installing and loading the required libraries**

```{r}
pacman::p_load(ggrepel, patchwork, 
               ggthemes, hrbrthemes,
               tidyverse) 
```

## 2.2 **Importing data**

```{r}
exam_data <- read_csv("Data/Exam_data.csv",show_col_types = FALSE)
head(exam_data)
str(exam_data)
```

## 2.3 **Beyond ggplot2 Annotation: ggrepel**

::: panel-tabset
# The Plot

```{r}
#| echo: False
ggplot(data=exam_data,
       aes(x=MATHS,
           y=ENGLISH))+
  geom_point()+
  geom_smooth(method=lm,
              size=0.5)+
  geom_label(aes(label=ID),
             hjust=0.5,
              vjust=-0.5)+
   coord_cartesian(xlim=c(0,100),
                    ylim=c(0,100)) 
ggtitle("English scores versus Maths scores for Primary 3")

```

## The code

```{r}
#| output: False
ggplot(data=exam_data,
       aes(x=MATHS,
           y=ENGLISH))+
  geom_point()+
  geom_smooth(method=lm,
              size=0.5)+
  geom_label(aes(label=ID),
             hjust=0.5,
              vjust=-0.5)+
   coord_cartesian(xlim=c(0,100),
                    ylim=c(0,100)) 
ggtitle("English scores versus Maths scores for Primary 3")
```
:::
